Model Recognition as Planning

### 2019-02-26 doc/icaps-19/camera-ready/model-recognition.tex
Fixed Miquel's email address
ICAPS19: fixed effects notation for open world assumption

%\author{\#92}
% Commented for blind submission
\author{Diego Aineto \and Sergio Jim\'enez\and Eva Onaindia\\
{\scriptsize Departamento de Sistemas Inform\'aticos y Computaci\'on}\\
{\scriptsize Universitat Polit\`ecnica de Val\`encia.}\\
{\scriptsize Camino de Vera s/n. 46022 Valencia, Spain}\\
{\scriptsize \{dieaigar,serjice,onaindia\}@dsic.upv.es}
\And Miquel Ram\'irez\\
{\scriptsize School of Computing and Information Systems}\\
{\scriptsize The University of Melbourne}\\
{\scriptsize Melbourne, Victoria. Australia}\\
{\scriptsize miquel.ramirez@nimelb.edu.au}}

@@

A {\em planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of \emph{actions}. An action $a\in A$ is defined with {\em preconditions}, $\pre(a)\in\mathcal{L}(F)$, {\em positive effects}, $\eff^+(a)\in\mathcal{L}(F)$, and {\em negative effects} $\eff^-(a)\in\mathcal{L}(F)$. The semantics of actions $a\in A$ is specified with two functions: $\rho(s,a)$ denotes whether action $a$ is {\em applicable} in a state $s$ and $\theta(s,a)$ denotes the {\em successor state} that results of applying action $a$ in a state $s$. Then, $\rho(s,a)$ holds iff $\pre(a)\subseteq s$. And the result of applying $a$ in $s$ is $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

@@

An action $a_c\in A$ with conditional effects is defined as a set of preconditions $\pre(a_c)\in\mathcal{L}(F)$ and a set of {\em conditional effects} $\cond(a_c)$. Each conditional effect $C\rhd E\in\cond(a_c)$ is composed of two sets of literals: $C\in\mathcal{L}(F)$, the {\em condition}, and $E\in\mathcal{L}(F)$, the {\em effect}. An action $a_c$ is applicable in a state $s$ if $\rho(s,a_c)$ is true, and the {\em triggered effects} resulting from the action application are the effects whose conditions hold in $s$:
\[
triggered(s,a_c)=\bigcup_{C\rhd E\in\cond(a_c),C\subseteq s} E,
\]

The result of applying action $a_c$ in state $s$ is $\theta(s,a_c)=\{s\setminus\eff_c^-(s,a))\cup\eff_c^+(s,a)\}$, where $\eff_c^-(s,a)\subseteq triggered(s,a)$ and $\eff_c^+(s,a)\subseteq triggered(s,a)$ are, respectively, the triggered {\em negative} and {\em positive} effects.

>>>>

%\author{\#92}
% Commented for blind submission
\author{Diego Aineto \and Sergio Jim\'enez\and Eva Onaindia\\
{\scriptsize Departamento de Sistemas Inform\'aticos y Computaci\'on}\\
{\scriptsize Universitat Polit\`ecnica de Val\`encia.}\\
{\scriptsize Camino de Vera s/n. 46022 Valencia, Spain}\\
{\scriptsize \{dieaigar,serjice,onaindia\}@dsic.upv.es}
\And Miquel Ram\'irez\\
{\scriptsize School of Computing and Information Systems}\\
{\scriptsize The University of Melbourne}\\
{\scriptsize Melbourne, Victoria. Australia}\\
{\scriptsize miquel.ramirez@unimelb.edu.au}}

@@

%A {\em planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of \emph{actions}. An action $a\in A$ is defined with {\em preconditions}, $\pre(a)\in\mathcal{L}(F)$, {\em positive effects}, $\eff^+(a)\in\mathcal{L}(F)$, and {\em negative effects} $\eff^-(a)\in\mathcal{L}(F)$. The semantics of actions $a\in A$ is specified with two functions: $\rho(s,a)$ denotes whether action $a$ is {\em applicable} in a state $s$ and $\theta(s,a)$ denotes the {\em successor state} that results of applying action $a$ in a state $s$. Then, $\rho(s,a)$ holds iff $\pre(a)\subseteq s$. And the result of applying $a$ in $s$ is $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

A {\em planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of \emph{actions}. An action $a\in A$ is defined with {\em preconditions}, $\pre(a)\in\mathcal{L}(F)$,  and {\em effects} $\eff(a)\in\mathcal{L}(F)$. The semantics of actions $a\in A$ is specified with two functions: $\rho(s,a)$ denotes whether action $a$ is {\em applicable} in a state $s$ and $\theta(s,a)$ denotes the {\em successor state} that results of applying action $a$ in a state $s$. Then, $\rho(s,a)$ holds iff $\pre(a)\subseteq s$. And the result of applying $a$ in $s$ is $\theta(s,a)=\{s\setminus\neg\eff(a))\cup\eff(a)\}$, with $\neg\eff(a) = \{\neg l : l \in \eff(a)\}$.

@@

%An action $a_c\in A$ with conditional effects is defined as a set of preconditions $\pre(a_c)\in\mathcal{L}(F)$ and a set of {\em conditional effects} $\cond(a_c)$. Each conditional effect $C\rhd E\in\cond(a_c)$ is composed of two sets of literals: $C\in\mathcal{L}(F)$, the {\em condition}, and $E\in\mathcal{L}(F)$, the {\em effect}. An action $a_c$ is applicable in a state $s$ if $\rho(s,a_c)$ is true, and the {\em triggered effects} resulting from the action application are the effects whose conditions hold in $s$:
%\[
%triggered(s,a_c)=\bigcup_{C\rhd E\in\cond(a_c),C\subseteq s} E,
%\]
%
%The result of applying action $a_c$ in state $s$ is $\theta(s,a_c)=\{s\setminus\eff_c^-(s,a))\cup\eff_c^+(s,a)\}$, where $\eff_c^-(s,a)\subseteq triggered(s,a)$ and $\eff_c^+(s,a)\subseteq triggered(s,a)$ are, respectively, the triggered {\em negative} and {\em positive} effects.

An action $a_c\in A$ with conditional effects is defined as a set of preconditions $\pre(a_c)\in\mathcal{L}(F)$ and a set of {\em conditional effects} $\cond(a_c)$. Each conditional effect $C\rhd E\in\cond(a_c)$ is composed of two sets of literals: $C\in\mathcal{L}(F)$, the {\em condition}, and $E\in\mathcal{L}(F)$, the {\em effect}. An action $a_c\in A$ is applicable in a state $s$ if and only if $\pre(a_c)\subseteq s$, and the {\em triggered effects} resulting from the action application are the effects whose conditions hold in $s$:
\[
triggered(s,a_c)=\bigcup\limits_{C\rhd E\in\cond(a_c),C\subseteq s} E. 
\]
The result of applying $a_c$ in state $s$ follows the same definition of successor state, $\theta(s,a)$, but applied to the conditional effects in $triggered(s,a_c)$.
